\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}

### 2021-09-22 paper/r1/manuscript-mssp.tex
gram

	\textcolor{r_s}{
	The other category is displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
	}

	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
	%基于GNSS的位移监测通常是可以通过时域差分来完成
	%GNSS定位结果可以来源于重复的静态测量结果，重复测量周期一般为一天到几个月，这类叫监测被称作长周期监测。
	%另外，也可以利用实时定位结果进行探测，已获得实时或者近实时的探测结果，这类被称作短周期探测。
	\textcolor{r_s}{
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. The positioning results can be obtained from repeated GNSS static measurements, and the repetition period is generally one day to several months. This kind of displacement detection is called long-term displacement detection. In addition, real-time or near real-time detection can be obtained by using GNSS kinematic positioning results, which is called short-term detection.}
	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which need to be defined in advance. 
	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}. This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}. Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
	The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
	The problem of displacement detection is to find out the time of displacement and estimate the displacement.

@@

	\begin{equation}\label{eq_bayesian_prior_tau_5}
	P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
	\end{equation}
	Through (\ref{eq_bayesian_prior_tau_basic}) and (\ref{eq_bayesian_prior_tau_5}), the joint probability of all change points can be determined. Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).  After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.

@@

	\subsection{Relative Real-time Kinematic (RTK)}
	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
	RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
}
	\subsection{Workflow of displacement detection }  
	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the \textcolor{r_s}{ kinematic positioning model is described.}
	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{Bayesian model for displacement detection.}
		\label{fig_v_workflow}
	\end{figure*}

@@

	\section{Experiments and Results}
	\label{exp}
	To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation and field experiments. 
	In the simulation experiment, the data is composed of designed displacement and noise.
	In the field experiment, the displacement is controlled manually by the  the self-built displacement control platform.
	Moreover, the results of some commonly used index-based abrupt detection methods including the Buishand U test(BUT), Pettitt’s test (PETT), standard normal homogeneity test (SNHT), Z test(ZT), are given for comparison.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_mu_sim_simple}
		\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
		\label{fig_v_mu_sim_simple}
	\end{figure} 
	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of Gaussian distribution of the histogram.
	Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
	The vertical green dashed line in Fig. \ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
	Among these means, $\mu_2$ has the highest accuracy, and its corresponding posterior sample coverage is the narrowest. 
	The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
	These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation. 
	As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
		\label{fig_v_bd9_4_up_tau}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
		\label{fig_v_bd9_4_up_mu}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
		\label{fig_v_bd9_4_up_sigma}
	\end{figure}
	Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
	It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
	Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
	In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
	In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
	\section{Discussion}
	\label{disc}
	In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
	In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
	Here, the interval between adjacent change points is constrained by adding a prior. 
	A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.

@@

	\begin{figure}[H]
		\centering
		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
		\caption{Bayesian model for displacement detection with an interval constraint prior.}
		\label{fig_v_simple_p_model_add_new_rule}
	\end{figure} 
	As shown in (\ref{eq_bayesian_prior_d_tau}) and Fig. \ref{fig_v_simple_p_model_add_new_rule}, the prior distribution of newly added random variables depends on the change points and the constraint interval. 
	In the following data processing, the interval $d$ is set to 300.
	The data in field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.

@@

	%从图16和图14的对比中可以看出，图14中t1次峰值得到了有效抑制，更加有利于主要变化点的识别。
	%此外，t2以及均值和方差的的后验分布没有明显变化。
	From the comparison between Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule} and Fig. \ref{fig_v_bd9_3_up_tau}, it can be seen that the secondary peak of $\tau_1$ posterior distribution in Fig. \ref{fig_v_bd9_3_up_tau} is effectively suppressed, which is more conducive to the identification of the primary change point. 
	There is no significant change in the posterior distribution of $\tau_2$, $\mu$, and  $\sigma$.
	The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Fig. \ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_exp2_idx}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.

>>>>

	\textcolor{r_s}{
	The other category is displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement \textcolor{r_s}{for} 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month field monitoring provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test and the control network processing results are generally based on repeated static adjustment.
	}

	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
	%基于GNSS的位移监测通常是可以通过时域差分来完成
	%GNSS定位结果可以来源于重复的静态测量结果，重复测量周期一般为一天到几个月，这类叫监测被称作长周期监测。
	%另外，也可以利用实时定位结果进行探测，已获得实时或者近实时的探测结果，这类被称作短周期探测。
	\textcolor{r_s}{
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. The positioning results can be obtained from repeated GNSS static measurements and the repetition period is generally one day to several months. This kind of displacement detection is called long-term displacement detection. In addition, real-time or near real-time detection can be obtained by using GNSS kinematic positioning results, which is called short-term detection.}
	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which \textcolor{r_s}{needs} to be defined in advance. 
	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}. This kind of method based on \textcolor{r_s}{a} statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}. Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of \textcolor{r_s}{coordinates}. The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.  
	The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
	The problem of displacement detection is to find out the time of displacement and estimate the displacement.

@@

	\begin{equation}\label{eq_bayesian_prior_tau_5}
	P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
	\end{equation}
	Through (\ref{eq_bayesian_prior_tau_basic}) and (\ref{eq_bayesian_prior_tau_5}), the joint probability of all change points can be determined. Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by \textcolor{r_s}{formulas} (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).  After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.

@@

	\subsection{Relative Real-time Kinematic (RTK)}
	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
	RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
}
	\subsection{Workflow of displacement detection }  
	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the \textcolor{r_s}{ kinematic positioning model is described.}
	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
	\begin{figure*}[htpb]
		\centering
		\includegraphics[scale=0.45]{v_workflow}
		\caption{\textcolor{r_s}{Displacement detection process based on Bayesian inference.}}
		\label{fig_v_workflow}
	\end{figure*}

@@

	\section{Experiments and Results}
	\label{exp}
	To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation and field experiments. 
	In the simulation experiment, the data is composed of designed displacement and noise.
	In the field experiment, the displacement is controlled manually by the self-built displacement control platform.
	Moreover, the results of some commonly used index-based abrupt detection methods including the Buishand U test(BUT), Pettitt’s test (PETT), standard normal homogeneity test (SNHT), Z test(ZT), are given for comparison.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_mu_sim_simple}
		\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
		\label{fig_v_mu_sim_simple}
	\end{figure} 
	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of \textcolor{r_s}{the} Gaussian distribution of the histogram.
	Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
	The vertical green dashed line in Fig. \ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
	Among these means, $\mu_2$ has the highest accuracy, and its corresponding posterior sample coverage is the narrowest. 
	The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
	These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation. 
	As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
		\label{fig_v_bd9_4_up_tau}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
		\label{fig_v_bd9_4_up_mu}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2.}
		\label{fig_v_bd9_4_up_sigma}
	\end{figure}
	Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
	It can be seen from Fig. \ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$. Unlike Fig. \ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s. 
	Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$. 
	In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
	In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
	\section{Discussion}
	\label{disc}
	In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point. 
	In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
	Here, the interval between adjacent change points is constrained by adding a prior. 
	A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.

@@

	\begin{figure}[H]
		\centering
		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
		\caption{ \textcolor{r_s}{Probability} model for displacement detection with an interval constraint prior.}
		\label{fig_v_simple_p_model_add_new_rule}
	\end{figure} 
	As shown in (\ref{eq_bayesian_prior_d_tau}) and Fig. \ref{fig_v_simple_p_model_add_new_rule}, the prior distribution of newly added random variables depends on the change points and the constraint interval. 
	In the following data processing, the interval $d$ is set to 300.
	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.

@@

	%从图16和图14的对比中可以看出，图14中t1次峰值得到了有效抑制，更加有利于主要变化点的识别。
	%此外，t2以及均值和方差的的后验分布没有明显变化。
	From the comparison between Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule} and Fig. \ref{fig_v_bd9_3_up_tau}, it can be seen that the secondary peak of $\tau_1$ posterior distribution in Fig. \ref{fig_v_bd9_3_up_tau} is effectively suppressed, which is more conducive to the identification of the primary change point. 
	There is no significant change in the posterior distribution of $\tau_2$, $\mu$, and  $\sigma$.
	The data in field experiment 2 is also reprocessed with the new \textcolor{r_s}{probability} model, and the results are shown in Fig. \ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_exp2_idx}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
